Collection of BAAD plots

### 2014-07-25 Rmd/baadplotscollection.Rmd
more analysis - very drafty!

allombygroupandpftplot <- function(xvar, yvar, studyName, xlab=AxisLabels[[xvar]], 
                                   ylab=AxisLabels[[yvar]], 
                                   slopecomp=1, n_min=20,legend=FALSE,
                                   pftcols=list(EA="red", EG="hotpink", DA="blue")){

  studyName$X <- studyName[,xvar]
  studyName$Y <- studyName[,yvar]

  smfitsEA <- sma(Y ~ X*Group, data=subset(studyName,pft=="EA"), 
                  log='xy', n_min=n_min, quiet=TRUE)
  smfitsEG <- sma(Y ~ X*Group, data=subset(studyName,pft=="EG"), 
                  log='xy', n_min=n_min, quiet=TRUE)
  smfitsDA <- sma(Y ~ X*Group, data=subset(studyName,pft=="DA"), 
                  log='xy', n_min=n_min, quiet=TRUE)
  smfits <- sma(Y ~ X*Group, data=studyName, log='xy', n_min=n_min, quiet=TRUE)

@@

AxisLabels <- list(m.to = "Total plant mass (kg)",
                   m.so = "Above-ground plant mass (kg)",
                   m.lf = "Total leaf mass (kg)",
                   m.rt = "Total root mass (kg)",
                   m.rf = "Fine root mass (kg)",
                   d.bh = "Diameter at breast height (m)",
                   d.ba = "Diameter at base (m)",
                   a.stbh = expression("Stem area at breast height"~~(m^2)),
                   a.stba = expression("Stem area at base"~~(m^2)),
                   a.lf = expression("Total leaf area"~~(m^2)),
                   h.t = "Total plant height (m)",
                   h.c = "Height to crown base (m)",
                   c.d = "Crown length (m)",
                   d.cr = "Crown diameter (m)")

@@

@@

>>>>

# basal area times height
baad2$a.stbh_h.t <- with(baad2, h.t * a.stbh)

allombygroupandpftplot <- function(xvar, yvar, data, xlab=AxisLabels[[xvar]], 
                                   ylab=AxisLabels[[yvar]], 
                                   slopecomp=1, n_min=20,legend=FALSE,
                                   pftcols=list(EA="red", EG="hotpink", DA="blue")){

  data$X <- data[,xvar]
  data$Y <- data[,yvar]

  smfitsEA <- sma(Y ~ X*Group, data=subset(data,pft=="EA"), 
                  log='xy', n_min=n_min, quiet=TRUE)
  smfitsEG <- sma(Y ~ X*Group, data=subset(data,pft=="EG"), 
                  log='xy', n_min=n_min, quiet=TRUE)

  smfitsDA <- sma(Y ~ X*Group, data=subset(data,pft=="DA"), 
                  log='xy', n_min=n_min, quiet=TRUE)

  smfits <- sma(Y ~ X*Group, data=data, log='xy', n_min=n_min, quiet=TRUE)

@@

AxisLabels <- list(m.to = "Total plant mass (kg)",
                   m.so = "Above-ground plant mass (kg)",
                   m.st = "Above-ground wood mass (kg)",
                   m.lf = "Total leaf mass (kg)",
                   m.rt = "Total root mass (kg)",
                   m.rf = "Fine root mass (kg)",
                   d.bh = "Diameter at breast height (m)",
                   d.ba = "Diameter at base (m)",
                   a.stbh = expression("Stem area at breast height"~~(m^2)),
                   a.stba = expression("Stem area at base"~~(m^2)),
                   a.lf = expression("Total leaf area"~~(m^2)),
                   h.t = "Total plant height (m)",
                   h.c = "Height to crown base (m)",
                   c.d = "Crown length (m)",
                   d.cr = "Crown diameter (m)",
                   a.stbh_h.t = expression("Stem area * height"~(m^3)))

@@

#allombygroupandpftplot("a.stbh_h.t", "m.st", baad2, slopecomp=1)

@@

allombygroupandpftplot("h.t", "m.st", baad2, legend=T, slopecomp=3)
allombygroupandpftplot("a.stbh", "m.st", baad2, legend=T, slopecomp=2)
allombygroupandpftplot("a.stbh", "h.t", baad2, legend=T, slopecomp=1/3)

```{r eval=FALSE}
df <- studyWithVars(baad2, c("m.st","a.stbh_h.t"))
x <- lapply(split(df,df$Group), function(x)try(lm(log10(m.st) ~ log10(a.stbh_h.t),data=x)))

getR2 <- function(x){
  if(inherits(x,"try-error"))
    NA
  else
    summary(x)$r.squared
}
